Practicing with Survival Analysis

### 2017-07-10 practice_survivalanalysis.Rmd
re-upload

hist(out1$time_until_answer)

@@

### estimating the cumulative hazard function
* H(t) = −log S(t), or can use the Nelson-Aalen estimator
* no function in survival package to do this
```{r}
#Kaplan Meier estimator of cumulative hazard
fit <- summary(survfit(surv_object ~ 1))
H.hat <- -log(fit$surv)
H.hat <- c(H.hat, tail(H.hat, 1)) #all this did was repeat the last entry?

@@

### mean, medians, percentiles
```{r}
#at 30,158 seconds, 50% of the questions have been answered
#mean survival time = 2,748,083
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)

#finding percentiles 
library(survival)
quantile(KM.obj, c(0.01, 0.10, 0.25, 0.50, 0.75, 0.95)) #Getting NA for 75 and 95 quantiles
quantile(KM.obj, 0.75)
```

>>>>

@@

### estimating the cumulative hazard function
* H(t) = −log S(t), or can use the Nelson-Aalen estimator
* no function in survival package to do this
* working with instructions from OpenIntro Survival analysis in r pdf 
```{r}
#Kaplan Meier estimator of cumulative hazard
fit <- summary(survfit(surv_object ~ 1))
H.hat <- -log(fit$surv)
H.hat <- c(H.hat, tail(H.hat, 1)) #all this did was repeat the last entry?

@@

### mean, medians, percentiles 
```{r}
#at 30,158 seconds (502.6 min), 50% of the questions have been answered
#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)

#finding percentiles 
library(survival)
quantile(KM.obj, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
#getting NA for 0.75 because our lowest S(t) = 0.3410254
```

* interpreting quantiles: 
* at time = 138 seconds (2.3 min), 1% of the questions have been answered
*           802 seconds (13.4 min), 10% of the questions have been answered
*           2,883 seconds (48.1 min), 25% of the questions have been answered

### exploring time_until_answered
* largest time_until_answered = 89.97 days (obs = 7807), and is censored
* shortest time_until_answered = 23 seconds (obs = 7485) 
```{r}
sum(out1$answered)/length(out1$answered)
#64.4% of observations are complete
#35.6% of observations are censored

library(ggplot2)
ggplot(out1, aes(x = time_until_answer)) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(20, 30000))
```
